\section{Related Work - Tracking}

\begin{frame}
	\frametitle{Related Work}
	\framesubtitle{Multi-Object Tracking}
	
	\Large
	
	\vspace{0.6cm}
	
	Multi-object tracking algorithms can be classified into two groups (Andriyenko et al.
	\cite{Andriyenko11}):
	
	\begin{itemize}
		\item \textbf{Global} (or \emph{offline}): formulating the tracking problem as an optimisation
			  one, where all the trajectories within a temporal window are optimised jointly
		\item \textbf{Recursive} (or \emph{online}): estimating the current state relying only on the
			  current observations and on the previous state
	\end{itemize}
	
	\vspace{0.82cm}
	
	\tiny
	
	\cite{Andriyenko11} A. Andriyenko \emph{et al.}, ``An analytical formulation of global occlusion
	reasoning for multi target tracking'', ICCV, 2011
\end{frame}

\begin{frame}
	\frametitle{Multi-Object Tracking}
	\framesubtitle{Global Methods}
	
	\Large
	
	\vspace{0.05cm}
	
	\begin{itemize}
		\item \textbf{Berclaz \emph{et al.} \cite{Berclaz11}}: mathematically sound multiple object
			  tracking framework based on a k-shortest path optimisation algorithm
		\item \textbf{Leal-Taix{\'e} \emph{et al.} \cite{Leal11}}: formulate a new graph model for
			  object tracking by minimising a network flow
		\item \textbf{Henriques \emph{et al.} \cite{Henriques11}}: propose a novel graph structure
			  that allows polynomial algorithms to obtain many-to-one and one-to-many optimal matchings
		\item ...
	\end{itemize}
	
	\vspace{0.15cm}
	
	\tiny
	
	\cite{Berclaz11} J. Berclaz \emph{et al.}, ``Multiple object tracking using k-shortest paths
	optimization'', PAMI, 2011
	
	\vspace{0.05cm}
	
	\cite{Leal11} L. Leal-Taix{\'e} \emph{et al.}, ``Everybody needs somebody: modeling social and
	grouping behavior on a linear programming multiple\\ \hspace{0.25cm} people tracker'', ICCV, 2011
	
	\vspace{-0.19cm}
	
	\cite{Henriques11} J. F. Henriques \emph{et al.}, ``Globally optimal solution to multi-object
	tracking with merged measurements'', ICCV, 2011
\end{frame}

\begin{frame}
	\frametitle{Multi-Object Tracking}
	\framesubtitle{Recursive Methods}
	
	\Large
	
	\vspace{0.05cm}
	
	\begin{itemize}
		\item \textbf{Breitenstein \emph{et al.} \cite{Breitenstein11}}: online method for
			  multi-person tracking-by-detection in a particle filtering framework
		\item \textbf{Bae \emph{et al.} \cite{Bae14}}: propose an online multiple object
			  tracking method based on tracklet confidence and online discriminative appearance learning
		\item \textbf{Yang \emph{et al.} \cite{Yang09}}: probabilistic appearance model
			  method for tracking multiple people
		\item ...
	\end{itemize}
	
	\vspace{0.15cm}
	
	\tiny
	
	\cite{Breitenstein11} M. D. Breitenstein \emph{et al.}, ``Online multiperson tracking-by-detection
	from a single, uncalibrated camera'', PAMI, 2011
	
	\vspace{0.05cm}
	
	\cite{Bae14} S. Bae \emph{et al.}, ``Robust online multi-object tracking based on tracklet
	confidence and online discriminative appearance\\ \hspace{0.25cm} learning'', CVPR, 2014
	
	\vspace{-0.19cm}
	
	\cite{Yang09} J. Yang \emph{et al.}, ``Probabilistic multiple people tracking through complex
	situations'', PETSW, 2009
\end{frame}

\begin{frame}
	\frametitle{Global vs Recursive Methods}
	
	\Large
	
	\vspace{0.1cm}
	
	\begin{table}[!t]
		\centering
		\begin{tabular}{ c | c | c | }
			\cline{2-3}
			& \textbf{Global} & \textbf{Recursive} \\ \hline
			
			\multicolumn{1}{|c|}{\textbf{Accuracy}} & medium/high & medium/high \\ \hline
			\multicolumn{1}{|c|}{\textbf{Precision}} & \textbf{high} & medium/high \\ \hline
			\multicolumn{1}{|c|}{\textbf{Robustness}} & \textbf{high} & medium/high \\ \hline
			\multicolumn{1}{|c|}{\textbf{Computational Load}} & high & \textbf{low}/medium \\ \hline
			\multicolumn{1}{|c|}{\textbf{Real-time}} & no & \textbf{yes}/no \\ \hline
		\end{tabular}
	\end{table}
	
	\vspace{0.15cm}
	
	Global methods are more precise and robust but they cannot be used in real systems:
	\begin{itemize}
		\item No information from the future is available
		\vspace{-0.1cm}
		\item Frame rate not suitable for real-time applications
	\end{itemize}
\end{frame}
